\section{Requirements}

\subsection{User Roles}


\subsubsection{Player}
A player is a user who has created an account and has access to view their own profile. A player can create games, join games, change their own password, add friends, message their friends and report other players. This user has no technical expertise and has standard level access.

\subsubsection{Admin}
An admin is a user who has an account created for them, granting them special permissions on sign in. In addition to having the same functionality as a player, the admin can, view reports, resolve reports and delete player accounts. An admin needs to be familiar with the technical no how of dealing with reports and has a high level of access.



\subsection{Functional Requirement User Stories and Tasks}

We chose to organize our user stories by user type and Story ID. Story ID's were organized alphabetically to easily find related user stories as well as improve readability.


\subsubsection{Player}

\textbf{A0: Log in to account (2)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want} to log into my account
    \item \textbf{So that} I can use my account
    \item \textbf{Definition of Done:} When the player can access their account
    \item \textbf{Depends On:} A1: Make an account
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ A0.1: login form. Create login form page.]]
        \item Task [[ A0.2: connect to database. authenticate credentials against backend credentials.]]
        \item Task [[ A0.3: Session management. create persistence for session that continues as user navigates the website.]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{A1: Make an account (2)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want} to make an account
    \item \textbf{So that} I can keep track of my stats
    \item \textbf{Definition of Done:} when the account is added to the database
    \item \textbf{Depends On:} Nothing
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ A1.1: Create registration form. Create page to make an account.]]
        \item Task [[ A1.2: Propogate account in database. make sure account generates in the DB.]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{A2: Update my account (2)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want} to update my account
    \item \textbf{So that} I can change my information
    \item \textbf{Definition of Done:} the database gets the update
    \item \textbf{Depends On:} A1: Make an account
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ A2.1: create update page. create form to update the users data.]]
        \item Task [[ A2.2: Modify database correctly. make sure the correct user is changed and data is updated in real time.]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{A3: Delete account (2)}
\begin{enumerate}
    \item Priority: Low
    \item \textbf{I want} to delete my account
    \item \textbf{So that} I can remove an account
    \item \textbf{Definition of Done:} When the account is removed from the database
    \item \textbf{Depends On:} A1: Make an account
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ A3.1: Admin panel to delete account. create the panel from which accounts can be deleted.]]
        \item Task [[ A3.2: Remove from database. ensure that user has been removed from database .]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{A4: Check account information (2)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want} to view account info/balance
    \item \textbf{So that} I know my balance
    \item \textbf{Definition of Done:} The player can see their account information
    \item \textbf{Depends On:} A1: Make an account
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ A4.1: create users page. Allow users to view their own profile]]
        \item Task [[ A0.1: Load session information. load correct information from user logged in, update from DB as it changes.]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{H0.1: Create Lobby (5)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want} to make a lobby
    \item \textbf{So that} other people can join
    \item \textbf{Definition of Done:} When the lobby is created and available to join
    \item \textbf{Depends On:} Nothing
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ H0.1.1: Create Lobby Form. Build a form to configure and create a lobby.]]
        \item Task [[ H0.1.2: Connect players. make sure players are connected to lobby so they can interact with each other.]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{H0.2: Start Game (5)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want} to start the game
    \item \textbf{So that} we can play the game
    \item \textbf{Definition of Done:} The game starts
    \item \textbf{Depends On:} H0.1: Create Lobby
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ H0.2.1: Create start game button. Button available to host of game to start]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{H0.3: Leave Game (1)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want} to leave the game
    \item \textbf{So that} I can get back to the home page
    \item \textbf{Definition of Done:} When I can go back to the home page and leave the game room
    \item \textbf{Depends On:} H0.1: Create Lobby, H0.2: Start Game, P7: Join Game
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ H0.3.1: Create button to leave game. Button to leave game]]
        \item Task [[ H0.3.2: Remove user from the lobby. Kick the user from the game and return them to the home screen.]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{P1: Play a card (5)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want} to place a card
    \item \textbf{So that} the game can progress
    \item \textbf{Definition of Done:} When a card leaves my hand
    \item \textbf{Depends On:} H0.2: Start Game
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ P1.1: Allow user to select card. Select card so it can be placed o top of deck]]
        \item Task [[ P1.2: Check if card can be placed on deck. Logic to define if card place is valid]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{P1.1: End Game (2)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want} to end the game
    \item \textbf{So that} I can get a win/loss
    \item \textbf{Definition of Done:} When the game ends and player stats are updated
    \item \textbf{Depends On:} H0.2: Start Game, P1: Play Card
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ P1.2: If user has no cards end game. Checks if cards are empty and ends game if so]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{P2: Draw a card (5)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want} to draw a card
    \item \textbf{So that} the game can progress
    \item \textbf{Definition of Done:} I get a new card in my hand
    \item \textbf{Depends On:} H0.2: Start Game
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ P2.1: User click on deck. Click on deck so they can draw card]]
        \item Task [[ P2.2: If deck is clicked, update users hand. adds card to users hand if deck is clicked]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{P5: Tutorial (1)}
\begin{enumerate}
    \item Priority: Low
    \item \textbf{I want} to learn the game
    \item \textbf{So that} I can understand the game
    \item \textbf{Definition of Done:} I am sent to the rules page
    \item \textbf{Depends On:} Nothing
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ P5.1: Create button to link of rules. Button is hyperlinked to external site that includes rules of the game ]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{P6: View Games (5)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want} to view all joinable games
    \item \textbf{So that} I can join a game
    \item \textbf{Definition of Done:} I can see all the joinable games
    \item \textbf{Depends On:} H0.1: Create Lobby
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ P6.1: Create games page. Create page to show games ]]
        \item Task [[ H6.2: Load games. Load list of all available games]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{P7: Join Game (8)}
\begin{enumerate}
    \item Priority: High
    \item \textbf{I want} to join a game
    \item \textbf{So that} to play with other users
    \item \textbf{Definition of Done:} When I join a lobby
    \item \textbf{Depends On:} H0.1: Create Lobby
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ P7.1: Create join game button. Button that joins game]]
        \item Task [[ P7.2: Check password. check to make sure game password is correct]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{P7.1: Connect Users to Game (2)}
\begin{enumerate}
    \item Priority: Low
    \item \textbf{I want} to join a game through my account
    \item \textbf{So that} I can keep track of my stats
    \item \textbf{Definition of Done:} When users are tracked by games
    \item \textbf{Depends On:} A1: Make an account, A0: Log in to account, H0.1: Create Lobby
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ P7.1.1: Connect to game. If password is correct, connect to lobby]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{P9: Ads (3)}
\begin{enumerate}
    \item Priority: Low
    \item \textbf{I want} to click on an ad
    \item \textbf{So that} I can go to the link
    \item \textbf{Definition of Done:} When I can go to the link for an ad by clicking it
    \item \textbf{Depends On:} Nothing
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ P9.1: Show ads on home page. display ads with hyperlink on homepage]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{P10: Send Message (5)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want} to send a message
    \item \textbf{So that} I can communicate with others
    \item \textbf{Definition of Done:} When user can DM other players
    \item \textbf{Depends On:} P13: Add friend
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ P10.1: View message modal. Display the message modal between friends]]
        \item Task [[ P10.2: Send content to DB. Send content entered in form to the database]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{P11: Read Message (5)}
\begin{enumerate}
    \item Priority: Medium
    \item \textbf{I want} to read my messages
    \item \textbf{So that} I can see what other players have DMed ne
    \item \textbf{Definition of Done:} When user can view all messages sent to them
    \item \textbf{Depends On:} A1: Make an account, P10: Send Message, P13: Add friend
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ P11.1: View message modal. Display the message modal between friends]]
        \item Task [[ P11.2: Load messages. Pull existing messages from the database]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{P12: Report (3)}
\begin{enumerate}
    \item Priority: Low
    \item \textbf{I want} to report another player
    \item \textbf{So that} bad accounts are seen by admins
    \item \textbf{Definition of Done:} When the report is sent
    \item \textbf{Depends On:} A1: Make an account
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ P12.1: Create report button. Button that opens form to report]]
        \item Task [[ P12.2: Send report form. Send form to database containing user and issue]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{P13: Add friend (3)}
\begin{enumerate}
    \item Priority: Low
    \item \textbf{I want} to add a friend
    \item \textbf{So that} I can ask someone to be a friend
    \item \textbf{Definition of Done:} When a friend request is sent
    \item \textbf{Depends On:} A0: Log in to account, A1: Make an account
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ P13.1: Create add friend button. Button that adds friend by username]]
        \item Task [[ P13.2: Logic to find friend in DB. Search database for username given]]
        \item Task [[ P13.3: Make friend request if friend found. If the username exists, create a friend request in that users friend request array in the database]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{P14: Accept friend (1)}
\begin{enumerate}
    \item Priority: Low
    \item \textbf{I want} to accept a friend request
    \item \textbf{So that} I can have a friend
    \item \textbf{Definition of Done:} Friends are saved in database and displayed on page
    \item \textbf{Depends On:} P13: Add friend
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ P14.1: Load friend requests. Form that shows and loads users friend requests]]
        \item Task [[ P14.2: Accept friend. button to accept and create friend relationship]]
        \item Task [[ P14.3: Remove friend request. Delete the friend request from DB now that it has been accepted]]
    \end{enumerate}
\end{enumerate}

\subsubsection{Admin}

\textbf{M2: Read player report (1)}
\begin{enumerate}
    \item Priority: Low
    \item \textbf{I want} to read a report
    \item \textbf{So that} I can check if a player is misbehaving
    \item \textbf{Definition of Done:} Report is read
    \item \textbf{Depends On:} P12: Report
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ M2.1: View reports. Load active reports into form]]
        \item Task [[ M2.2: Resolve report. Button that removes report from database once resolved]]
    \end{enumerate}
\end{enumerate}

\vspace{2em}

\textbf{M4: Change password (3)}
\begin{enumerate}
    \item Priority: Low
    \item \textbf{I want} to change my password
    \item \textbf{So that} my account stays safe
    \item \textbf{Definition of Done:} When password is changed in the database
    \item \textbf{Depends On:} A1: Make an account
    \item Tasks:
    \begin{enumerate}
    % For each task write the ID, :, then title. Then describe the task.
        \item Task [[ M4.1: View users button. Shows all active users and their ids]]
        \item Task [[ M4.2: Button to change password on each user. Button that opens form to change password of said user]]
        \item Task [[ M4.3: Save changes. Saves changed password to the DB]]
    \end{enumerate}
\end{enumerate}